Single-step Hybrid Predition

### 2017-01-09 reports/methods.Rmd
Use tmp path for temporary BGLR output

# Data Overview
```{r setup-overview, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble", "purrr")

>>>>

# Methods
## Genetic Material and Phenotyping
```{r setup-overview, message = FALSE, echo = FALSE}
if (!require("pacman")) install.packages("pacman")
pacman::p_load("data.table", "ggplot2", "ggthemes", "dplyr", "forcats", 
               "viridis", "tidyr", "knitr", "tibble", "purrr")
